Iterative Reduction: Parsing and Interpreting Code Without Trees

### 2024-12-16 Paper/paper.tex
comments to the second exmaple

We define our alphabet $\Sigma$ to be the same as in~\Cref{sec:firstattempt}.
Now we define our initial $\beta$-reducer which will support parentheses.
It is an extension of our previous $\beta$-reducer:
\begin{gather*}
    \hb(\mbt x,\mb\circ) = (\mb{\ttt x,\circ},\snd),\quad \hb(\mb{\ttt x,\circ},\mbt y) = (\mb{\ttt x\circ\ttt y},\snd) \qquad \hbox{for $\circ\in\set{\ttt{+,*}}$} \\
    \hb(\mbt{x,*},\mbt{y,+}) = (\mbt{x*y,+},\snd)
\end{gather*}
where $\fst,\snd$ are the first and second projections, respectively (i.e. $(x,y)\mapsto x$ and $(x,y)\mapsto y$).
We then add the rules for parentheses:
\begin{gather*}
    \hb(\mbt x,\mbt)) = (\mbt{x,)},\snd),\quad \hb{\mb{\ttt x,\circ},\mbt{y,)}} = (\mb{\ttt x\circ\ttt y,\ttt)},\snd) \qquad \hbox{for $\circ\in\set{\ttt{+,*}}$} \\
    \hb(\mbt(,\mbt{x,)}) = (\mbt x,\fst)
\end{gather*}
\gobble) % syntax highlighting
And we define our priority function as follows:
\[ \pi(\mbt x) = \infty\hbox{ for numbers \ttt x},\quad \pi(\mbt+) = 1,\quad \pi(\mbt*) = 2,\quad \pi(\mbt() = \infty,\quad \pi(\mbt)) = 0 \]

@@

>>>>

\begin{example}
We define our alphabet $\Sigma$ to be the same as in~\Cref{sec:firstattempt}.
Now we define our initial $\beta$-reducer which will support parentheses.
It is an extension of our previous $\beta$-reducer:
\begin{gather*}
    \hb(\mbt x,\mb\circ) = (\mb{\ttt x,\circ},\snd),\quad \hb(\mb{\ttt x,\circ},\mbt y) = (\mb{\ttt x\circ\ttt y},\snd) \qquad \hbox{for $\circ\in\set{\ttt{+,*}}$} \\
    \hb(\mbt{x,*},\mbt{y,+}) = (\mbt{x*y,+},\snd)
\end{gather*}
where $\fst,\snd$ are the first and second projections, respectively (i.e. $(x,y)\mapsto x$ and $(x,y)\mapsto y$).
We then add the rules for parentheses:
\begin{gather*}
    \hb(\mbt x,\mbt)) = (\mbt{x,)},\snd),\quad \hb{\mb{\ttt x,\circ},\mbt{y,)}} = (\mb{\ttt x\circ\ttt y,\ttt)},\snd) \qquad \hbox{for $\circ\in\set{\ttt{+,*}}$} \\
    \hb(\mbt(,\mbt{x,)}) = (\mbt x,\fst)
\end{gather*}
\gobble) % syntax highlighting
And we define our priority function as follows:
\yoni{feels out of context, the notion of a priority function
was not defined. Also, notice that some tokens get priorities and some don't, which is a bit confusing.}
\[ \pi(\mbt x) = \infty\hbox{ for numbers \ttt x},\quad \pi(\mbt+) = 1,\quad \pi(\mbt*) = 2,\quad \pi(\mbt() = \infty,\quad \pi(\mbt)) = 0 \]

@@

\end{example}
